Flowchart of Current Algorithm

### 2009-04-23 docs/flowchart/flowchart.tex
done hooking in the w0 stuff for spherical

We integrate
\begin{equation}
\frac{\partial w_0}{\partial r} =  \Sbar - \frac{1}{\gammabar p_0} \psi
\enskip \label{eq:divw0} ,
\end{equation}
with the following discretization:
\begin{equation}
\frac{\partial w_0^{\outp}}{\partial r} =  \Sbar^{\inp}
- \frac{1}{\gammabar^{\inp} p_0^{\inp}}\psi^{\inp}
\enskip .
\end{equation}
% VOLUME DISCREPANCY STUFF
%\begin{equation}
%\frac{\partial w_0^{\nph,\star}}{\partial r} =  \overline{S^{\nph,\star}}
%- \frac{1}{\gammabar^{n} p_0^{n}}
%\left\{ \psi^{\nmh} + 
%f \left[\frac{p_0^n - \overline{p(\rho,h,X_k)^n}}{\Delta t^n} \right]\right\}
%\enskip .
%\end{equation}

@@

We begin with equation (23) in paper III written in spherical coordinates:
\[
\frac{1}{r^2}\frac{\partial}{\partial r} \left (r^2 \beta_0 w_0 \right ) =
\beta_0 \left ( \Sbar - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} \right )\enskip.
\]
We expand the spatial derivative and divide through by $\beta_0$:
\begin{equation}
\label{eq:sphconstraint}
\frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 w_0 \right ) +
w_0 \frac{1}{\beta_0} \frac{\partial \beta_0}{\partial r} =
 \Sbar - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t}  \enskip .
\end{equation}
Recalling from paper I that;
\[
\frac{1}{\gammabar p_0}  \frac{\partial p_0}{\partial r} = \frac{1}{\beta_0} \frac{\partial \beta_0}{\partial r}\enskip,
\]
and moving this term to the right hand side,
we can express equation (\ref{eq:sphconstraint}) as:
\begin{eqnarray}
\frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 w_0 \right ) &=&
  \Sbar - \frac{1}{\gammabar p_0} \left( 
\frac{\partial p_0}{\partial t} + w_0 \frac{\partial p_0}{\partial r} \right)\enskip. \label{eq:w01}
\end{eqnarray}
We first solve a piece of this equation for $\ow = w_0 - \dw$:
\begin{eqnarray}
\frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 \ow \right ) &=& \Sbar \enskip.
\end{eqnarray}
Then we can write
\begin{eqnarray}
\frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 \dw \right ) &=&
  - \frac{1}{\gammabar p_0} \left[
\frac{\partial p_0}{\partial t} + (\ow + \dw)
\frac{\partial p_0}{\partial r} \right]\enskip.\label{eq:w01a}
\end{eqnarray}

@@

\noindent We discretize this elliptic equation in the radial dimension as:
\begin{eqnarray}
&& \frac{1}{\Delta r} \left\{
\left[ \frac{\gammabar p_0}{r^2} \frac{\partial (r^2 \dw)}{\partial r} \right]_{j} -
\left[ \frac{\gammabar p_0}{r^2} \frac{\partial (r^2 \dw)}{\partial r} \right]_{j-1} \right\}
+ \left[ \frac{4 (r^2 \dw) \rho_0 g}{r^3} \right]_{j-\myhalf} \nonumber\\
&=& 
- \frac{g_{j-\myhalf}}{r_{j-\myhalf}^2 \Delta r} 
\left[ \left( r^2 \etarho \right)_{j} - \left( r^2 \etarho  \right)_{j-1} \right] 
   - \left( \frac{4 \ow \rho_0 g}{r} \right)_{j-\myhalf}
   - \left(  4 \pi G \rhozero \etarho   \right)_{j-\myhalf} \enskip , \nonumber
\end{eqnarray}
where we have chosen to solve for $(r^2 \dw)$ rather than $\dw.$
Then, using hydrostatic equilibrium, we expand this to 
\begin{eqnarray}
&& \frac{1}{\Delta r} \left\{
 \left( \frac{\gammabar p_0}{r^2}\right)_{j  } \frac{\left[ (r^2 \dw)_{j+\myhalf} - (r^2 \dw)_{j-\myhalf} \right]}{\Delta r}
-\left( \frac{\gammabar p_0}{r^2}\right)_{j-1} \frac{\left[ (r^2 \dw)_{j-\myhalf} - (r^2 \dw)_{j-\thalf}\right]}{\Delta r} \right\} \nonumber \\
&&  - \left( \frac{4}{r_{j-\myhalf} ^3} \frac{p_{0,i} - p_{0,i-1}}{\dr} \right) (r^2 \dw)_{j-\myhalf}  \nonumber \\
&=&   \left( \frac{4}{r_{j-\myhalf} ^3} \frac{p_{0,i} - p_{0,i-1}}{\dr} \right) (r^2 \ow)_{j-\myhalf}
 - \frac{g_{j-\myhalf}}{r_{j-\myhalf}^2 \Delta r} 
  \left[ \left( r^2 \etarho \right)_{j} - \left( r^2 \etarho  \right)_{j-1} \right] 
- \left(  4 \pi G \rhozero \etarho   \right)_{j-\myhalf} \enskip. \nonumber \\
\end{eqnarray}

If we write this in matrix form, so that:
\begin{equation}
A_j (r^2 \dw)_{j-\thalf} + B_j (r^2 \dw)_{j-\myhalf} + C_j (r^2 \dw)_{j+\myhalf} = F_j\enskip,
\end{equation}
then:
\begin{eqnarray}
A_j &=& \frac{1}{\Delta r^2} \left( \frac{\gammabar p_0}{r^2}\right)_{j-1}  \enskip, \nonumber  \\
B_j &=& -\frac{1}{\Delta r^2} \left[ \left( \frac{\gammabar p_0}{r^2}\right)_{j  }  
               +\left( \frac{\gammabar p_0}{r^2}\right)_{j-1} \right] 
              - \left( \frac{4}{r_{j-\myhalf} ^3} \frac{p_{0,i} - p_{0,i-1}}{\dr} \right) \nonumber \\
C_j &=& \frac{1}{\Delta r^2} \left( \frac{\gammabar p_0}{r^2}\right)_{j}  \enskip, \nonumber  \\
F_j &=&  \left( \frac{4}{r_{j-\myhalf} ^3} \frac{p_{0,i} - p_{0,i-1}}{\dr} \right) (r^2 \ow)_{j-\myhalf}
 - \frac{g_{j-\myhalf}}{r_{j-\myhalf}^2 \Delta r} 
\left[ \left( r^2 \etarho \right)_{j} - \left( r^2 \etarho  \right)_{j-1} \right] 
- \left(  4 \pi G \rhozero \etarho   \right)_{j-\myhalf} \enskip \nonumber .
\end{eqnarray}
Here,
\begin{equation}
g_{j-\myhalf} = \frac{G}{r_{j-\myhalf}^2} \sum_{k=1}^{j} \frac{4}{3} \pi  (r_{k-\myhalf}^3 - r_{k-\thalf}^3) \; {\rho_0}_{k-1} \enskip.
\end{equation}

We define the lower boundary condition, $ \dw = 0$ at $r=0,$ which
corresponds to $j=1,$ by setting:
\begin{eqnarray}
A_1 = C_1 = F_1 &=& 0\enskip, \nonumber \\
B_1 &=& 1\enskip. \nonumber
\end{eqnarray}
We also specify $\partial (r^2 \dw) / \partial r = 0$ at the the upper boundary, which corresponds to $j=N,$
by setting:
\begin{eqnarray}
A_N &=& -1\enskip, \nonumber \\
B_N &=&  1\enskip, \nonumber \\
C_N = F_N &=& 0\enskip. \nonumber
\end{eqnarray}
\end{description}

@@

If this is the first step of the calculation ($n=0$), we set
\begin{equation}
S^{\myhalf,\star} = \frac{S^0 + S^1}{2} \enskip ,
\end{equation}
where $S^1$ is found through the iterative process that initializes the calculation.
Otherwise, following the method used in our small-scale low Mach number algorithm
(BDRWZ), we extrapolate to the half-time using the source
terms at the previous and current time levels
\begin{equation}
S^{\nph,\star} = S^n + \frac{\Delta t^n}{2} \frac{S^n - S^{n-1}}{\Delta t^{n-1}} \enskip .
\end{equation}

\item Compute
\begin{equation}
\overline{S^{\nph,\star}} = {\mathrm{\bf Avg}} \left(S^{\nph,\star}\right) \enskip .
\end{equation}

\item {\bf Compute $w_0$ Planar}$[\overline{S^{\nph,\star}},\gammabar^n,p_0^n,\psi^{n-\myhalf}]
\rightarrow [w_0^{n+\myhalf,*}]$

\item Using 
\begin{equation}
- \frac{1}{\rho_0} \frac{\partial \pizero}{\partial r} 
= \frac{\partial w_0}{\partial t} + w_0 \frac{\partial w_0}{\partial r} 
\enskip, \label{eq:pizero}
\end{equation}
define the scaled pressure gradient
\begin{equation}
-\left ( \frac{1}{\rho_0^n} \frac{\partial \pizeroone}{\partial r} \right ) = 
\frac{w_0^{\nph,\star} - w_0^\nmh}{(\dt^n+\dt^{n-1})/2} 
+  w_0^{n,\star} \left(\frac{\partial w_0}{\partial r}\right)^{n,\star} \enskip ,
\end{equation} 
where $w_0^{n,\star}$ and $(\partial w_0 / \partial r)^{n,\star}$ are
\begin{equation}
w_0^{n,\star} = \frac{\dt^{n} w_0^{\nmh} + \dt^{n-1} w_0^{\nph,\star}}{\dt^n+\dt^{n-1}} 
\enskip,\end{equation}
\begin{equation}
\left(\frac{\partial w_0}{\partial r}\right)^{n,\star} = 
\frac{1}{\dt^n+\dt^{n-1} } 
\left [ \dt^{n} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nmh}
+ \dt^{n-1} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nph,\star} \right ] 
\enskip.\end{equation}
If $n=0$, we use $\dt^{-1} = \dt^0$.

@@

\item First, define:
\begin{equation}
\gammabar^{\nph,\star} = \frac{\gammabar^{n} + \gammabar^{n+1,\star}}{2}\enskip ,
\end{equation}
\begin{equation}
p_0^{\nph,\star} = \frac{p_0^{n} + p_0^{n+1,\star}}{2}\enskip .
\end{equation}
{\bf Compute $w_0$ Planar}$[\overline{S^{\nph,\star}},\gammabar^{\nph,\star},p_0^{\nph,\star},
\psi^{\nph,\star}] \rightarrow [w_0^{\nph}]$.
% VOLUME DISCREPANCY STUFF
%\begin{equation}
%\overline{p(\rho,h,X_k)^{\nph,\star}} = 
%\frac{\overline{p(\rho,h,X_k)^n} + \overline{p(\rho,h,X_k)^{n+1,\star}}}{2}\enskip .
%\end{equation}
%\begin{equation}
%\frac{\partial w_0^{\nph}}{\partial r} = 
%\overline{S^{\nph}} - \frac{1}{\gammabar^{\nph,\star} p_0^{\nph,\star}}
%\left\{ \psi^{\nph,\star} + f \left[\frac{p_0^{\nph,\star} - \overline{p(\rho,h,X_k)^{\nph,\star}}}{\Delta t^n}\right]\right\}
%\enskip ,

\item Using equation (\ref{eq:pizero}), define
\begin{equation}
-\left ( \frac{1}{\rho_0^n} \frac{\partial \pizerotwo}{\partial r} \right ) = 
\frac{w_0^{\nph} - w_0^\nmh}{\myhalf(\dt^n+\dt^{n-1})} 
+ w_0^n \left(\frac{\partial w_0}{\partial r}\right)^n.
\end{equation}
where $w_0^n$ and $(\partial w_0 / \partial r)^{n}$ are defined through paper III equation (53),
\begin{equation}
w_0^{n,\star} = \frac{\dt^{n} w_0^{\nmh} + \dt^{n-1} w_0^{\nph,\star}}{\dt^n+\dt^{n-1}}\enskip,\label{eq:w0nstar}
\end{equation}
and paper III equation (54),
\begin{equation}
\left(\frac{\partial w_0}{\partial r}\right)^{n,\star} = \frac{1}{\dt^n+\dt^{n-1} } \left [ \dt^{n} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nmh}
+ \dt^{n-1} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nph,\star} \right ] \enskip.\label{eq:dw0drnstar}
\end{equation}

>>>>

We integrate
\begin{equation}
\frac{\partial w_0}{\partial r} =  \Sbar - \frac{1}{\gammabar p_0} \psi
\enskip \label{eq:divw0} ,
\end{equation}
with the following discretization:
\begin{equation}
\frac{\partial w_0^{\outp}}{\partial r} =  \Sbar^{\inp}
- \frac{1}{\gammabar^{\inp} p_0^{\inp}}\psi^{\inp}
\enskip ,
\end{equation}
and $w_0=0$ at $r=0$.
% VOLUME DISCREPANCY STUFF
%\begin{equation}
%\frac{\partial w_0^{\nph,\star}}{\partial r} =  \overline{S^{\nph,\star}}
%- \frac{1}{\gammabar^{n} p_0^{n}}
%\left\{ \psi^{\nmh} + 
%f \left[\frac{p_0^n - \overline{p(\rho,h,X_k)^n}}{\Delta t^n} \right]\right\}
%\enskip .
%\end{equation}

@@

We begin with equation (23) in paper III written in spherical coordinates:
\[
\frac{1}{r^2}\frac{\partial}{\partial r} \left (r^2 \beta_0 w_0 \right ) =
\beta_0 \left ( \Sbar - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} \right )\enskip.
\]
We expand the spatial derivative and divide through by $\beta_0$:
\begin{equation}
\label{eq:sphconstraint}
\frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 w_0 \right ) +
w_0 \frac{1}{\beta_0} \frac{\partial \beta_0}{\partial r} =
 \Sbar - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t}  \enskip .
\end{equation}
Recalling from paper I that;
\[
\frac{1}{\gammabar p_0}  \frac{\partial p_0}{\partial r} = \frac{1}{\beta_0} \frac{\partial \beta_0}{\partial r}\enskip,
\]
and moving this term to the right hand side,
we can express equation (\ref{eq:sphconstraint}) as:
\begin{eqnarray}
\frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 w_0 \right ) &=&
  \Sbar - \frac{1}{\gammabar p_0} \left( 
\frac{\partial p_0}{\partial t} + w_0 \frac{\partial p_0}{\partial r} \right)\enskip. \label{eq:w01}
\end{eqnarray}
We first solve a piece of this equation for $\ow = w_0 - \dw$:
\begin{eqnarray}
\frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 \ow \right ) &=& \Sbar^{\inp} \enskip.
\end{eqnarray}
Then we can write
\begin{eqnarray}
\frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 \dw \right ) &=&
  - \frac{1}{\gammabar p_0} \left[
\frac{\partial p_0}{\partial t} + (\ow + \dw)
\frac{\partial p_0}{\partial r} \right]\enskip.\label{eq:w01a}
\end{eqnarray}

@@

\noindent We discretize this elliptic equation in the radial dimension as:
\begin{eqnarray}
&& \frac{1}{\Delta r} \left\{
\left[ \frac{\gammabar p_0}{r^2} \frac{\partial (r^2 \dw)}{\partial r} \right]_{j} -
\left[ \frac{\gammabar p_0}{r^2} \frac{\partial (r^2 \dw)}{\partial r} \right]_{j-1} \right\}
+ \left[ \frac{4 (r^2 \dw) \rho_0 g}{r^3} \right]_{j-\myhalf} \nonumber\\
&=& 
- \frac{g_{j-\myhalf}}{r_{j-\myhalf}^2 \Delta r} 
\left[ \left( r^2 \etarho \right)_{j} - \left( r^2 \etarho  \right)_{j-1} \right] 
   - \left( \frac{4 \ow \rho_0 g}{r} \right)_{j-\myhalf}
   - \left(  4 \pi G \rhozero \etarho   \right)_{j-\myhalf} \enskip , \nonumber
\end{eqnarray}
where we have chosen to solve for $(r^2 \dw)$ rather than $\dw.$
Then, using hydrostatic equilibrium, we expand this to 
\begin{eqnarray}
&& \frac{1}{\Delta r} \left\{
 \left( \frac{\gammabar p_0}{r^2}\right)_{j  } \frac{\left[ (r^2 \dw)_{j+\myhalf} - (r^2 \dw)_{j-\myhalf} \right]}{\Delta r}
-\left( \frac{\gammabar p_0}{r^2}\right)_{j-1} \frac{\left[ (r^2 \dw)_{j-\myhalf} - (r^2 \dw)_{j-\thalf}\right]}{\Delta r} \right\} \nonumber \\
&&  - \left( \frac{4}{r_{j-\myhalf} ^3} \frac{p_{0,j} - p_{0,j-1}}{\dr} \right) (r^2 \dw)_{j-\myhalf}  \nonumber \\
&=&   \left( \frac{4}{r_{j-\myhalf} ^3} \frac{p_{0,j} - p_{0,j-1}}{\dr} \right) (r^2 \ow)_{j-\myhalf}
 - \frac{g_{j-\myhalf}}{r_{j-\myhalf}^2 \Delta r} 
  \left[ \left( r^2 \etarho \right)_{j} - \left( r^2 \etarho  \right)_{j-1} \right] 
- \left(  4 \pi G \rhozero \etarho   \right)_{j-\myhalf} \enskip, \nonumber \\
\end{eqnarray}
where $\etarho$ at cell-centers is the average of the neighboring edge-values.

If we write this in matrix form, so that:
\begin{equation}
A_j (r^2 \dw)_{j-\thalf} + B_j (r^2 \dw)_{j-\myhalf} + C_j (r^2 \dw)_{j+\myhalf} = F_j\enskip,
\end{equation}
then:
\begin{eqnarray}
A_j &=& \frac{1}{\Delta r^2} \left( \frac{\gammabar^{\inp} p_0^{\inp}}{r^2}\right)_{j-1}  \enskip, \nonumber  \\
B_j &=& -\frac{1}{\Delta r^2} \left[ \left( \frac{\gammabar^{\inp} p_0^{\inp}}{r^2}\right)_{j  }  
               +\left( \frac{\gammabar^{\inp} p_0^{\inp}}{r^2}\right)_{j-1} \right] 
              - \left( \frac{4}{r_{j-\myhalf} ^3} \frac{p_{0,j}^{\inp} - p_{0,j-1}^{\inp}}{\dr} \right) \nonumber \\
C_j &=& \frac{1}{\Delta r^2} \left( \frac{\gammabar^{\inp} p_0^{\inp}}{r^2}\right)_{j}  \enskip, \nonumber  \\
F_j &=&  \left( \frac{4}{r_{j-\myhalf} ^3} \frac{p_{0,j}^{\inp} - p_{0,j-1}^{\inp}}{\dr} \right) (r^2 \ow)_{j-\myhalf}
 - \frac{g_{j-\myhalf}}{r_{j-\myhalf}^2 \Delta r} 
\left[ \left( r^2 \etarho^{\inp} \right)_{j} - \left( r^2 \etarho^{\inp}  \right)_{j-1} \right] 
- \left(  4 \pi G \rhozero^{\inp} \etarho^{\inp}   \right)_{j-\myhalf} \enskip \nonumber .
\end{eqnarray}
Here,
\begin{equation}
g_{j-\myhalf} = \frac{G}{r_{j-\myhalf}^2} \sum_{k=1}^{j} \frac{4}{3} \pi  (r_{k-\myhalf}^3 - r_{k-\thalf}^3) \; \rho_{0,k-1}^{\inp} \enskip.
\end{equation}

We define the lower boundary condition, $ \dw = 0$ at $r=0,$ which
corresponds to $j=1,$ by setting:
\begin{eqnarray}
A_1 = C_1 = F_1 &=& 0\enskip, \nonumber \\
B_1 &=& 1\enskip. \nonumber
\end{eqnarray}
We also specify $\partial (r^2 \dw) / \partial r = 0$ at the the upper boundary, which corresponds to $j=N,$
by setting:
\begin{eqnarray}
A_N &=& -1\enskip, \nonumber \\
B_N &=&  1\enskip, \nonumber \\
C_N = F_N &=& 0\enskip. \nonumber
\end{eqnarray}
Finally, $w_0^{\outp} = \ow + \delta w_0$.
\end{description}
\end{enumerate}

@@

If this is the first step of the calculation ($n=0$), we set
\begin{equation}
S^{\myhalf,\star} = \frac{S^0 + S^1}{2} \enskip ,
\end{equation}
where $S^1$ is found through the iterative process that initializes the calculation.
Otherwise, following the method used in our small-scale low Mach number algorithm
(BDRWZ), we extrapolate to the half-time using the source
terms at the previous and current time levels
\begin{equation}
S^{\nph,\star} = S^n + \frac{\Delta t^n}{2} \frac{S^n - S^{n-1}}{\Delta t^{n-1}} \enskip .
\end{equation}
\item Compute
\begin{equation}
\overline{S^{\nph,\star}} = {\mathrm{\bf Avg}} \left(S^{\nph,\star}\right) \enskip .
\end{equation}
\item Compute $w_0^{n+\myhalf,*}$:
\begin{description}
\item[plane-parallel:]{\bf Compute $w_0$ Planar}$[\overline{S^{\nph,\star}},
\gammabar^n,p_0^n,\psi^{n-\myhalf}]\rightarrow [w_0^{n+\myhalf,*}]$.
\item[spherical:]{\bf Compute $w_0$ Spherical}$[\overline{S^{\nph,\star}},\gammabar^n,
\rhozero^n,p_0^n,\etarho^{n-\myhalf}] \rightarrow [w_0^{n+\myhalf,*}]$.
\end{description}

\item Define the scaled pressure gradient using
\begin{equation}
- \frac{1}{\rho_0} \frac{\partial \pizero}{\partial r} 
= \frac{\partial w_0}{\partial t} + w_0 \frac{\partial w_0}{\partial r} 
\enskip, \label{eq:pizero}
\end{equation}
with the following discretization:
\begin{equation}
-\left ( \frac{1}{\rho_0^n} \frac{\partial \pizeroone}{\partial r} \right ) = 
\frac{w_0^{\nph,\star} - w_0^\nmh}{(\dt^n+\dt^{n-1})/2} 
+  w_0^{n,\star} \left(\frac{\partial w_0}{\partial r}\right)^{n,\star} \enskip ,
\end{equation} 
where $w_0^{n,\star}$ and $(\partial w_0 / \partial r)^{n,\star}$ are
\begin{equation}
w_0^{n,\star} = \frac{\dt^{n} w_0^{\nmh} + \dt^{n-1} w_0^{\nph,\star}}{\dt^n+\dt^{n-1}} 
\enskip,\end{equation}
\begin{equation}
\left(\frac{\partial w_0}{\partial r}\right)^{n,\star} = 
\frac{1}{\dt^n+\dt^{n-1} } 
\left [ \dt^{n} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nmh}
+ \dt^{n-1} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nph,\star} \right ] 
\enskip.\end{equation}
If $n=0$, we use $\dt^{-1} = \dt^0$.

@@

\item Define:
\begin{equation}
\gammabar^{\nph,\star} = \frac{\gammabar^{n} + \gammabar^{n+1,\star}}{2}\enskip , ~~~
\rhozero^{\nph,\star} = \frac{\rhozero^{n} + \rhozero^{n+1,\star}}{2}\enskip , ~~~
p_0^{\nph,\star} = \frac{p_0^{n} + p_0^{n+1,\star}}{2}\enskip .
\end{equation}
\item Compute $w_0^{n+\myhalf}$:
\begin{description}
\item[plane-parallel:]{\bf Compute $w_0$ Planar}$[\overline{S^{\nph}},
\gammabar^{n+\myhalf,*},p_0^{n+\myhalf,*},\psi^{n+\myhalf,\star}]\rightarrow [w_0^{n+\myhalf,*}]$.
\item[spherical:]{\bf Compute $w_0$ Spherical}$[\overline{S^{\nph}},\gammabar^{n+\myhalf,*},
\rhozero^{n+\myhalf,*},p_0^{n+\myhalf,*},\etarho^{n+\myhalf,\star}] \rightarrow [w_0^{n+\myhalf}]$.
\end{description}
% VOLUME DISCREPANCY STUFF
%\begin{equation}
%\overline{p(\rho,h,X_k)^{\nph,\star}} = 
%\frac{\overline{p(\rho,h,X_k)^n} + \overline{p(\rho,h,X_k)^{n+1,\star}}}{2}\enskip .
%\end{equation}
%\begin{equation}
%\frac{\partial w_0^{\nph}}{\partial r} = 
%\overline{S^{\nph}} - \frac{1}{\gammabar^{\nph,\star} p_0^{\nph,\star}}
%\left\{ \psi^{\nph,\star} + f \left[\frac{p_0^{\nph,\star} - \overline{p(\rho,h,X_k)^{\nph,\star}}}{\Delta t^n}\right]\right\}
%\enskip ,

\item Using equation (\ref{eq:pizero}), define the scaled pressure gradient using the
following discretization:
\begin{equation}
-\left ( \frac{1}{\rho_0^n} \frac{\partial \pizerotwo}{\partial r} \right ) = 
\frac{w_0^{\nph} - w_0^\nmh}{\myhalf(\dt^n+\dt^{n-1})} 
+ w_0^n \left(\frac{\partial w_0}{\partial r}\right)^n.
\end{equation}
where $w_0^n$ and $(\partial w_0 / \partial r)^{n}$ are defined through paper III equation (53),
\begin{equation}
w_0^{n,\star} = \frac{\dt^{n} w_0^{\nmh} + \dt^{n-1} w_0^{\nph,\star}}{\dt^n+\dt^{n-1}}\enskip,\label{eq:w0nstar}
\end{equation}
and paper III equation (54),
\begin{equation}
\left(\frac{\partial w_0}{\partial r}\right)^{n,\star} = \frac{1}{\dt^n+\dt^{n-1} } \left [ \dt^{n} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nmh}
+ \dt^{n-1} \left(\frac{\partial w_0 }{ \partial r}\right)^{\nph,\star} \right ] \enskip.\label{eq:dw0drnstar}
\end{equation}
